%%
%% UW CBE Thesis: chapterfivename/chapterfivename.tex
%% Written by Ankur Gupta, Sep 1, 2013
%% Departament of Chemical and Biological Engineering
%% University of Wisconsin-Madison
%% Copyright (c) Ankur Gupta, 2014
%%
%% License: GPL v3. See LICENSE.
%%

% This is Chapter 5. You're now over the hump.
% Drive it home.
\chapter{Chapter Five Title}
\label{chap:chapterfivename}
\doublespacing

\section{Defining shortcuts}
\label{sec:chapterfivename:defining_shortcuts}

You will notice that I have a \texttt{shortcuts.tex} file in this thesis template folder. 
This file is then \texttt{input}ted in the file \texttt{uwcbethesis-config.tex}. 
The \texttt{shortcuts.tex} file contains many shortcuts that are going to be used 
repeatedly throughout in the thesis. For example, \verb+\chaptertwoname{}+ is a 
shortcut defined in \texttt{shortcuts.tex} file. \\

I have also defined many math symbols that I have to use repeatedly. The following 
equations use these commands. \\

The following equation describes a $n$-dimensional random vector, $\bfX$
\begin{align}
\bfX \sim \fN \left( \mu, \Sigma \right)
\end{align}
distributed normally with mean vector $\mu$ and covariance matrix $\Sigma$. The 
probability density of $\bfX$ is given by 
\begin{align}
f_{\bfX}(\bfx) = \frac{1}{(2\pi)^{\frac{n}{2}} \abs{\Sigma}^{\frac{1}{2}}}\text{ } e^{-\frac{1}{2} (\bfx-\mu)^{T} \Sigma^{-1} (\bfx-\mu)}
\end{align}



\section{Using \texttt{uwcbethesis-config.tex}}
\label{sec:chapterfivename:using_config_file}

Instead of typing out your name, department, title of your thesis, etc. 
this thesis template defines this data all at once in the file named
\texttt{uwcbethesis-config.tex}. Please make use of these commands instead 
of repeatedly typing out the data. Not only does this help reduce the number 
of typographical errors, it enforces homogeneity. This thesis template uses 
the commands defined in this config file. 


